Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-09-12 scagnostics.Rmd
Small fixes only.

```{r findpipe, fig.width=6, fig.height=7, fig.cap="Guided tour optimising TIC index for Pipe 1000 dataset.", echo=FALSE}
set.seed(2018)
pipeResc <- rescale(pipe1000) #unselect 2 variables to make optimisation easier
pipeTour <- save_history(pipeResc,
                         guided_tour(mineIndex("TIC"), search_f = tourr:::search_better,
                                     cooling=1, alpha = 0.5, max.tries = 5000))
pipeTourFull <- as.list(interpolate(pipeTour))
pipeTourRes <- getProj(pipe1000, pipeTourFull, "Pipe", 1000)
pipeTourResMelt <- melt(pipeTourRes, id=c("t", "name", "size"))
ggplot(pipeTourResMelt, aes(x=t, y=value)) +
  geom_line() + 
  facet_wrap(~variable, ncol=1, scales = "free_y")
```

```{r testpipe}

iLast <- length(pipeTourFull)
fProj <- pipeTourFull[[iLast]]
dProj <- as.tibble(pipeResc %*% fProj)
ggplot(dProj, aes(V1,V2)) + geom_point()
```

@@

```{r testpipe2}
iLast <- length(pipeTourFull)
fProj <- pipeTourFull[[iLast]]
dProj <- as.tibble(pipeResc %*% fProj)
ggplot(dProj, aes(V1,V2)) + geom_point()
```

>>>>

```{r findpipe, echo=FALSE}
set.seed(2018)
pipeResc <- rescale(pipe1000) #unselect 2 variables to make optimisation easier
pipeTour <- save_history(pipeResc,
                         guided_tour(mineIndex("TIC"), search_f = tourr:::search_better,
                                     cooling=1, alpha = 0.5, max.tries = 5000))
pipeTourFull <- as.list(interpolate(pipeTour))
```

```{r pipeFirstRun,fig.width=6, fig.height=7, fig.cap="Guided tour optimising MIC index for Pipe 1000 dataset.", echo=FALSE}
pipeTourRes <- getProj(pipe1000, pipeTourFull, "Pipe", 1000)
pipeTourResMelt <- melt(pipeTourRes, id=c("t", "name", "size"))
ggplot(pipeTourResMelt, aes(x=t, y=value)) +
  geom_line() + 
  facet_wrap(~variable, ncol=1, scales = "free_y")
```

```{r testpipe}
iLast <- length(pipeTourFull)
fProj <- pipeTourFull[[iLast]]
dProj <- as.tibble(pipeResc %*% fProj)
ggplot(dProj, aes(V1,V2)) + geom_point()
```

@@

```{r testpipe2}
iLast <- length(pipeTourFull2)
fProj <- pipeTourFull2[[iLast]]
dProj <- as.tibble(pipeResc %*% fProj)
ggplot(dProj, aes(V1,V2)) + geom_point()
```
